Transfer learning between Sentinel-1 acquisition modes enhances \\ the few-shot segmentation of natural oil slicks in the Arctic

### 2025-04-06 latex/manuscript.tex
conclusion structure

\section{Conclusion}
Applications of transfer learning must be carefully evaluated. In many cases, its use can be inefficient, even detrimental, if the contexts are too different \cite{mensinkFactorsInfluenceTransfer2022}.
In this study, we made use of labeled slicks from a different area and imaged in a different SAR acquisition mode. We show that transfer learning in the form of fine-tuning is effective for the few-shot SAR segmentation
of natural oil slicks, improving model performance (average Dice increase of 0.03--0.13) despite accessing only a few examples in the target domain. 
Indeed, both deep learning models benefited from transferring pretrained model weights, 
with DeepLabv3 performing best overall, though SAM achieved top accuracy with fewer training images.

>>>>

\section{Conclusion}
Applications of transfer learning must be carefully evaluated. In many cases, its use can be inefficient, even detrimental, if the contexts are too different \cite{mensinkFactorsInfluenceTransfer2022}.
In this study, we made use of labeled slicks from a different area and imaged in a different SAR acquisition mode. We show that transfer learning in the form of fine-tuning is effective for the few-shot SAR segmentation
of natural oil slicks, improving model performance (average Dice increase of 0.03--0.13), while accessing only a few examples in the target domain. 
Both deep learning models benefited from transferring pretrained model weights, 
with DeepLabv3 performing best overall, though SAM achieved top accuracy with fewer training images.
